Firstly, I would like to thank my advisor Yann LeCun for believing in
unsupervised learning both for machines and students. His unwaivering
enthusiasm and commitment to tackling the hard problems inspired many to make
steady progress in this emerging area of research.

I thank many colleagues that have passed through our lab over the years. 
Particularly, Joan Bruna who tough me that patient, deliberate thought is the
surest way to find structure in chaos.  I thank Jonathan Tompson for being a
great friend and showing me what it means to be a truly great
multi-disciplinary engineer.  I owe a debt of gratitude to David Eigen, who
provided invaluable insight to many hard problems. My thanks to the
neuroscience folks ``across the street'', Eero Simoncelli and his lab members,
for providing many insightful discussions. Many thanks to Julian Panetta for
his patient help in everything from proof-reading papers to answering many
``embarrassing'' computer science related questions. Thanks to Michael Mathieu 
for being an incredibly talented collaborator and researcher.     
      
I'm thankful to my old friends Mohammad and Ramzy for providing their
friendship, guidance, support, and encouragement over many years.  Thanks to my
friend William from Georgia Tech for always being available for a chat and
advice.  I thank my friends and colleagues at NSWC-PCD (particularly my friend
and mentor, Quyen Huynh) for their many years of support and encouragement.
Finally, I'm grateful to my parents who have always encouraged me to pursue my
passions and disregard the rest. I'm also grateful to my parents for being
patient and supportive through my many years in school.  Last, but certainly
not least, thank you Emer for your loving support.  

 
