This work would not have been possible without the guidance and support of many people, both friends and colleges alike.

Firstly, I would like to thank my family for the many years of love and support; for being understanding of an overly curious child prone to taking things apart without putting them back together. In particular I would like to thank my mother and father, Diane and Phillip, for eventually teaching me how to put it all back together.

I would like to thank Ken Perlin for teaching me the value of truly creative thinking and for showing me how a powerful imagination can drive successful research. I would also like to thank my advisor, Chris Bregler, for many hours spent proof reading conference submissions at the last minute and for making the whole process a fun and enjoyable experience. Many thanks to Yann LeCun, who was a constant source of key insights and invaluable advice, which has help me learn the intuitions that led to much of the work in this thesis.

Of course there are also many students at NYU who deserve a huge amount of credit for helping me through my PhD. I would like to thank Murphy Stein for helping me learn to ask the right questions. I owe a debt of gratitude to Arjun Jain for many, many hours of insightful discussions, as well as helping me find all those annoying bugs. I would like to thank Ross Goroshin for teaching me about auto-encoders and all things ``unsupervised'' and I would like to thank Kristofer Schlachter for our shared love of computer graphics.

Lastly, I owe a huge debt of gratitude to Alberto Lerner for teaching me the importance of detailed-oriented engineering. I am absolutely certain that I would still be a terrible coder if not for your patience, understanding and ``tough love'' code reviews.
